Yoghurt under stress

### 2014-06-18 seminaire_Tanakalab.tex
Viscosity

\againframe<3>{carpet}
\tikzset{external/force remake}
\begin{frame}{Cell thickness}
\begin{tikzpicture}[mark size={0.3em}]
	\matrix[matrix of nodes, inner sep=0, column sep=0.01\columnwidth, row sep=0.01\columnwidth, ampersand replacement=\&] (m) {
		\includegraphics[width=0.245\columnwidth]{pattern_50um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_100um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_250um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left=0.01\columnwidth and 0 of m.south east] (x800) {\includegraphics[width=0.49\columnwidth]{pattern_800um_x1.jpg}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.196\columnwidth, 0.05\columnwidth) -- ++(0.145\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[line width=0.2em,Main](x800.north east) -- ++(-0.217\columnwidth,0) node[midway,below] {\SI{5}{\milli\metre}};

	\begin{axis}[%
		name=g,
		anchor=left of north west,
		at={($(m.south west)+(0,-0.01\columnwidth)$)},
		scale only axis,
		width=0.5\textwidth-3em,
		height=0.25\columnwidth-2em,
		xmin=0,xmax=1,xlabel={$e$ (\si{\milli\metre})},
		xtick={0,0.4,...,0.9},
		ymin=0,ylabel={$\lambda$ (\si{\milli\metre})},
		]
		\addplot[no marks, domain=0:3] {4.23*x};
		\begin{scope}[inner sep=0, minimum size=0.8em]
			\node[circle, fill=Accent1] at (axis cs:0.05,0.261){};
			\node[circle, fill=white, draw=Accent1] at (axis cs:0.1,0.458) {};
			\node[regular polygon, regular polygon sides=3, fill=Accent1] at (axis cs:0.250,0.916){};
			\node[regular polygon, regular polygon sides=3, fill=white, draw=Accent1] at (axis cs:0.450,2.075){};
			\node[fill=Accent1] at (axis cs:0.800,3.333){};
		\end{scope}
	\end{axis}
	\begin{scope}[inner sep=0, minimum size=0.8em, transform canvas={xshift=0.5em, yshift=-0.5em}]
		\node[circle, fill=Accent1] at (m-1-1.north west) {};
		\node[circle, fill=white, draw=Accent1] at (m-1-2.north west){};
		\node[regular polygon, regular polygon sides=3, fill=Accent1] at (m-1-3.north west){};
		\node[regular polygon, regular polygon sides=3, fill=white, draw=Accent1] at (m-1-4.north west) {};
		\node[fill=Accent1] at (x800.north west) {};
	\end{scope}
\end{tikzpicture}
\end{frame}
\tikzset{external/force remake=false}

>>>>

\againframe<3>{carpet}

%\tikzset{external/force remake}
\begin{frame}{Cell thickness}
\begin{tikzpicture}[mark size={0.3em}]
	\matrix[matrix of nodes, inner sep=0, column sep=0.01\columnwidth, row sep=0.01\columnwidth, ampersand replacement=\&] (m) {
		\includegraphics[width=0.245\columnwidth]{pattern_50um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_100um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_250um.jpg}\&
		\includegraphics[width=0.245\columnwidth]{pattern_450um.jpg}\\
	};
	\node[inner sep=0, below left=0.01\columnwidth and 0 of m.south east] (x800) {\includegraphics[width=0.49\columnwidth]{pattern_800um_x1.jpg}};
	\draw[ultra thick, Accent2, <->] (x800.south west) ++(0.196\columnwidth, 0.05\columnwidth) -- ++(0.145\columnwidth,0) node[midway,above]{$\lambda$};
	\draw[line width=0.2em,Main](x800.north east) -- ++(-0.217\columnwidth,0) node[midway,below] {\SI{5}{\milli\metre}};

	\begin{axis}[%
		name=g,
		anchor=left of north west,
		at={($(m.south west)+(0,-0.01\columnwidth)$)},
		scale only axis,
		width=0.5\textwidth-3em,
		height=0.25\columnwidth-2em,
		xmin=0,xmax=1,xlabel={$e$ (\si{\milli\metre})},
		xtick={0,0.4,...,0.9},
		ymin=0,ylabel={$\lambda$ (\si{\milli\metre})},
		]
		\addplot[no marks, domain=0:3] {4.23*x};
		\begin{scope}[inner sep=0, minimum size=0.8em]
			\node[circle, fill=Accent1] at (axis cs:0.05,0.261){};
			\node[circle, fill=white, draw=Accent1] at (axis cs:0.1,0.458) {};
			\node[regular polygon, regular polygon sides=3, fill=Accent1] at (axis cs:0.250,0.916){};
			\node[regular polygon, regular polygon sides=3, fill=white, draw=Accent1] at (axis cs:0.450,2.075){};
			\node[fill=Accent1] at (axis cs:0.800,3.333){};
		\end{scope}
	\end{axis}
	\begin{scope}[inner sep=0, minimum size=0.8em, transform canvas={xshift=0.5em, yshift=-0.5em}]
		\node[circle, fill=Accent1] at (m-1-1.north west) {};
		\node[circle, fill=white, draw=Accent1] at (m-1-2.north west){};
		\node[regular polygon, regular polygon sides=3, fill=Accent1] at (m-1-3.north west){};
		\node[regular polygon, regular polygon sides=3, fill=white, draw=Accent1] at (m-1-4.north west) {};
		\node[fill=Accent1] at (x800.north west) {};
	\end{scope}
\end{tikzpicture}
\end{frame}
%\tikzset{external/force remake=false}

\tikzset{external/force remake}
\begin{frame}{Surprising viscosity influence}
\begin{columns}
\column{0.5\textwidth}
\[ \lambda^* \sim \left(\frac{B \ell_p^2}{\eta v h}\right)^\frac{1}{3}\]
\begin{tikzpicture}
	\begin{loglogaxis}[%
		width=\textwidth,
		height=0.8\textwidth,
		xmin=0.6,xmax=11,xlabel={viscosity (\si{\milli\pascal\second})},
		xtick={0.7, 1, 2, 5, 10}, xticklabels={$0.7$, $1$, $2$, $5$, $10$},
		ytick={1,2,3,4}, yticklabels={$1$,$2$,$3$,$4$},
		ymin=1, ymax=5, ylabel={$\lambda$ (\si{\milli\metre})},
		mark size={0.3em},
		legend style={legend pos=south east},
		]
		\addplot+[no marks, domain=0.7:10, black, forget plot] {1.7*x^0.4} node[midway, below] {$\eta^{0.4}$};
		\addplot+[only marks,Accent1, mark=o] table{eta_lambda_eau_pure.txt};
		\addplot+[only marks,Accent2, mark=square] table{eta_lambda_eau_glycerol.txt};
		\legend{water, water-glycerol};
	\end{loglogaxis}
\end{tikzpicture}

\column{0.5\textwidth}
\begin{itemize}
\item $\lambda$ increases with $\eta$
\item Can be explained only by a hidden dependence of the viscosity on $B$, $\ell_p$, \ldots 
\item[$\Rightarrow$] Viscosity influences gel formation.
\end{itemize}
%If $\ell_p \sim \eta^{-\alpha}$ and $B\sim \mathrm{k_B}T \left(\frac{h}{\ell}\right)^3$, then
%\[ \lambda^* \sim \eta^\frac{\alpha-1}{3} \]
%\[\alpha\simeq 2.2\]
\end{columns}
\end{frame}

\begin{frame}{Viscosity of the solvent during gel formation}
\begin{tabu}{X[c]X[c]}
water $\eta=\SI{1}{\milli\pascal\second}$ &
glycerol 60\% $\eta=\SI{10}{\milli\pascal\second}$\\
\includegraphics[width=0.45\textwidth]{XYslice_gly0}&
\includegraphics[width=0.45\textwidth]{XYslice_gly60}
\end{tabu}
\tikz\draw[line width=0.2em] (0,0) -- ++(0.045\textwidth,0) node[midway, below] {\SI{10}{\micro\metre}};
\end{frame}
